---
title: "SWELL calibration tutorial"
author: "GeoModel lab"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SWELL calibration tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This `html_vignette` explains how to perform the calibration of the `SWELL` model for NDVI and EVI simulation. 

## Preparing climate and vegetation data 

The `SWELL` model uses daily air temperature and latitude as input to estimate photothermal responses of vegetation to reproduce the dynamics of a remote sensing index via calibration. The two sources of information needed are then:
- vegetation index data: the Normalized Difference Vegetation Index (NDVI) and the Enhanced Vegetation Index (EVI) are current options.
- climate data: daily maximum and minimum air temperature (°C) 

The climate data are downloaded by the NASA-Power database as an example. 
The vegetation data refer to hazelnut orchards in Turkey from NASA MODIS satellite.  These data are accessible in the `hazelnut_data` dataframe, but can also be downloaded via the `MODIStools` package, as explained at the end of this vignette.


```{r_install, fig.show='hold'}

#load SWELL library
library(SWELL)

?vegetation_data


```



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
